\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-12 paper.qmd
Updated Figure 12 ordering

To illustrate how the methods organise difference number of points within the structure in the NLDR layout, simulated $7\text{-}D$ data having C-shaped structure is used.

>>>>

To illustrate how the methods organize difference number of points within the structure in the NLDR layout, simulated $7\text{-}D$ data having C-shaped structure is used.

### 2025-01-12 paper.tex
Updated Figure 12 ordering

To illustrate how the methods organise difference number of points
within the structure in the NLDR layout, simulated \(7\text{-}D\) data
having C-shaped structure is used.

>>>>

To illustrate how the methods organize difference number of points
within the structure in the NLDR layout, simulated \(7\text{-}D\) data
having C-shaped structure is used.
